\section{Background}\label{sec:background}
\subsection{Different expectations in a company}
Often in the different company's they have a different structure and information of what a CV could have in their application.
Most of the time the companies expectations can be related to work experience and education,
and a CV could either be long or short depends on which company the person is writing to. Some people can write a long CV,
but it isn't necessarily a good CV, and people can write a short one but it isn't good enough. 
Both of these statements could have some information that are not relevant to the company's requirement. Still there are some other
factors that can be included, and some companies´would love to know what the person did in that particular year. 
In that particular situation would be different from company to company, since those people who are working with humanities 
can have human related criteria for getting a job in this area. The same goes for IT where they have more work with a computer
than any other people, because these jobs immerse themselves everyday with it. According to Computerworld it-jobbank, 
they have actually analyzed a total 6700 job-advertisements in the year of 2015 and 2019 where the company was sorting all categories
that are related to IT, and they have published the top 10. It is shown between those years that the job-advertisements
have more of a technical and a more professional knowledgeable than before, since more
https://www.it-jobbank.dk/om-jobsoegning/karrierecenter/viden-om/it-karriere/disse-10-personlige-kompetencer-efterspoerger-virksomhederne?audiencetagid=140

Technical
Structured
Professional knowledge
Strong
Dynamic
Analytical
Responsible
Outgoing
Curious
Professional \\

Structured
Technical
Dynamic
Strong
Informal
Responsible
Professional
Outgoing
Analytical
Committed

Header: Include the Principal Investigator’s (PI’s) full name in the top left corner of the page header on every page. \\
Margins: Use at least half-inch margins. The header may fall within the top margin, but the body text should not begin closer than one half-inch from the edge of the page.
Font: Use size 11 Calibri for the main body of the text. Figures, tables and captions may be size 8 font.
Page Numbering: Each page must be numbered consecutively for each PDF upload. Each section of an uploaded document must begin with page 1.
Spacing: Use single spacing.
Document Format: Upload all attachments in PDF format.