{\selectlanguage{english}
\aautitlepage{%
  \englishprojectinfo{
     P0-Projektet %title
  }{%
    CV - generation valg %theme
  }{%
    Efterårssemestret 2020 %project period
  }{%
    SW 1 Gruppe 005 Klynge 1 % project group
  }{%
    %list of group members
    David Doctor Heyde Rasmussen \\
    Hans Erik Heje\\ 
    Mikkel Kaa\\
    Ming Hui Sun
  }{%
    %list of supervisors
    Johannes Bjerva
  }{%
    18. december 2020 % date of completion
  }%
}{%department and address
  \textbf{Software}\\
  Aalborg Universitet\\
  \href{http://www.aau.dk}{http://www.aau.dk}
}{% the abstract
  This project is going to focus on the theme "Digital CV" 
  which this project will find a problem for those people who struggle with making a CV,
  and the reasons behind the rejection. It is well-established that networking is very common to get a job in most countries, 
  and even when people are sending a lot of CVs to different companies 
  there is still a good chance of it being rejected by all of them.
  The project aims to find a software solution for those who are in need of a better CV 
  and a better chance for getting past the ATS scanner and hiring personnel.\\
  To test if the software solution was a success, 
  a job counselor was assigned to check one CV from a human and 15 different CVs from a computer with 15 different job postings; comparing them
  to determine which of these were most likely to get an interview from the specific job position. 
  The feedback concluded that structure and contents were essential to get a good result and only one of them did the program succeed in.
  Lacking the adequate capabilities to structure  CV as fluently as a human, might deter the hiring personal. Despite this, the ATS scanner was a success 
  because of the final products filtering capabilities.

  The process of applying for a job can be strenuous and time consuming. 
  Especially for the unemployed, there potential wasted by a process the seemingly unfair.
  This project objective to create a C program that can produce Digital CV, that will aid the unemployed in obtaining a job.
  The program will be built with the purpose of producing a large quantity Digital CV´s that could passing two employer screening systems, the ATS Scanner and hiring personnel.
  To test is our projects Digital CV was a success, we compared a CV created by our program to a CV written by human hands. 
  During the project two tests were conducted, to evaluate if the Digital CV fulfilled the projects objective.
  One for the ATS scanner and one for one the hiring personnel.
  The test results were mixed, with the Digital CV having moderate success at passing the hiring personnel, though poor success at passing the ATS scanner.
  These results indicate that the projects objective was not fully meet.






  This project is going to focus on the theme "Digital CV" 
  which this project will find a problem for those people who struggle with making a CV,
  and the reasons behind the rejection. Especially for the unemployed, there potential wasted by a process the seemingly unfair.
  The project aims to find a software solution that can produce Digital CV 
  and will aid for higher chance of getting past the ATS scanner and hiring personnel.
  During the project two tests were conducted, to evaluate if the Digital CV fulfilled the projects objective.
  One for the ATS scanner and one for one the hiring personnel. 
  The feedback concluded that structure and contents were essential to get a good result and only one of them did the program succeed in.
  Lacking the adequate capabilities to structure  CV as fluently as a human, might deter the hiring personal. Despite this, the ATS scanner was a success 
  because of the final products filtering capabilities.
}}